---
title: "Increase rate of belgian population density by region between 1992 and 2019"
description: |
  This post will explore the increase rate of the belgian population density by region between 1992 and 2019.
author:
  - name: Guillaume Gégo
    url: {}
date: 11-16-2020
categories:
  - "Demography"
  - "Data Science 1"
preview: SpaceBiology1.jpg
output:
  distill::distill_article:
    self_contained: false
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

#Importation des données

SciViews::R

bx <- read$rds("data/region_bxl_av_2000.rds")

bx2 <- read$rds("data/region_bxl_ap_2000.rds")

rw <- read$csv("data/region_wallonne_av_2000.csv")

rw2 <- read$csv("data/region_wallonne_ap_2000.csv")

rf <- read$xls("data/region_flamande_av_2000.xls")

rf2 <- read$xls("data/region_flamande_ap_2000.xls")

#Transformation des données

bruxelles <- full_join(bx, bx2) 

wallonie <- full_join(rw, rw2)

flandre <- full_join(rf, rf2)

#Assemblage des différents tableaux

belgique1 <- bind_rows(bruxelles, wallonie, flandre)

belgique <- pivot_longer(belgique1, cols = c(population_au_01_janvier_1992 : population_au_01_janvier_2019), names_to = "années", values_to = "population")
rmarkdown::paged_table(belgique)

write$rds(belgique, file = "data/belgique.rds")

# Import du DF
belgique <- read$rds("data/belgique.rds")
  
belgique -> belgique1
  
# On remplace population_au_01_janvier_ par du rien
str_replace(belgique1$années, "population_au_01_janvier_", "") -> Pannées
  
# On renomme les colonnes et on remplace année par Purification années (Pannées)
belgique1 %>.%
  select(., - c(années)) %>.%
  mutate(., Pannées = c(Pannées)) -> belgique_clean
  
names(belgique_clean) <- c("tranches", "region", "sexe", "nationalite", "population", "annees")

# Conversions spéciales
belgique_clean$tranches <- ordered(belgique_clean$tranches, levels = c("Moins de 18 ans", "De 18 à 64 ans", "65 ans et plus"))
```
  
```{r}
# Création de jeu de donnée attirés pour la population par année en Wallonie
belgique_clean %>.%
  filter(., region %in% c("Région wallonne")) %>.%
  group_by(., annees) %>.%
  summarise(., "poptot_w" = sum(population)) -> belgique_w
  
# Création de jeu de donnée attirés pour la population par année en Flandre
belgique_clean %>.%
  filter(., region %in% c("Région flamande")) %>.%
  group_by(., annees) %>.%
  summarise(., "poptot_f" = sum(population)) -> belgique_f
  
# Création de jeu de donnée attirés pour la population par année en région de bruxelles capitale
belgique_clean %>.%
  filter(., region %in% c("Région de Bruxelles-Capitale")) %>.%
  group_by(., annees) %>.%
  summarise(., "poptot_bc" = sum(population)) -> belgique_bc
  
# Création de jeu de donnée attirés pour la population par année en Belgique
belgique_clean %>.%
  group_by(., annees) %>.%
  summarise(., "poptot" = sum(population), superf_b = 30689)-> belgique_poptot_sup

  
# Initialisation de variables
superf_b = 30689
superf_f = 13625
superf_w = 16901
superf_bc = 161.4
  

# Création de jeu de donnée attirés pour le pourcentage d'augmentation densité de population par région au cours du temps
belgique_w %>.%
  mutate(., "densite_w" = (poptot_w/superf_w)) %>.%
  select(., - poptot_w) -> bel_w_dense

belgique_f %>.%
  mutate(., "densite_f" = (poptot_f/superf_f)) %>.%
  select(., - poptot_f) -> bel_f_dense

belgique_bc %>.%
  mutate(., "densite_bc" = (poptot_bc/superf_bc)) %>.%
  select(., - poptot_bc) -> bel_bc_dense

belgique_poptot_sup %>.%
  mutate(., "densite_b" = (poptot/superf_b), "region" = "Belgique total") -> bel_dense

# V2 
belgique_clean %>.%
  group_by(., annees, region) %>.%
  summarise(., "poptot" = sum(population)) -> belgique_regan

belgique_regan %>.%
  filter(., region %in% c("Région flamande")) %>.%
  mutate(., "densite_f" = (poptot/superf_f)) -> belgique_f_dense

belgique_regan %>.%
  filter(., region %in% c("Région wallonne")) %>.%
  mutate(., "densite_w" = (poptot/superf_w)) -> belgique_w_dense

belgique_regan %>.%
  filter(., region %in% c("Région de Bruxelles-Capitale")) %>.%
  mutate(., "densite_bc" = (poptot/superf_bc)) -> belgique_bc_dense

belgique_poptot_sup %>.%
  mutate(., "densite_b" = (poptot/superf_b), "region" = "Belgique total") -> bel_dense
  
bel_d1 <- full_join(belgique_regan, belgique_f_dense, by = c("poptot", "region", "annees"))
  
bel_d2 <- full_join(bel_d1, belgique_w_dense, by = c("poptot", "region", "annees"))
  
bel_d3 <- full_join(bel_d2, belgique_bc_dense, by = c("poptot", "region", "annees"))
  
belgique_densite <- full_join(bel_d3, bel_dense, by = c("poptot", "region", "annees"))

belgique_densite %>.%
  mutate(., 
    densite_f2 = str_replace_na(densite_f,replacement = ""),
    densite_w2 = str_replace_na(densite_w,replacement = ""),
    densite_bc2 = str_replace_na(densite_bc,replacement = ""),
    densite_b2 = str_replace_na(densite_b,replacement = "")
  ) %>%
  mutate(
    densite = str_c(densite_f2, densite_w2, densite_bc2, densite_b2)
  ) -> belgique_densite_clean

belgique_densite_clean <- select(belgique_densite_clean, - c("densite_f", "densite_w", "densite_bc", "densite_b", "densite_f2", "densite_w2", "densite_bc2", "densite_b2", "superf_b"))

# V3
belgique_bc_dense %>.%
  select(., - poptot) %>.%
  mutate(., per_densite_bc = ((round(densite_bc, digits = 2) - 5893.54)/5893.54) * 100) -> belgique_per_densite_bc
  
belgique_w_dense %>.%
  select(., - poptot) %>.%
  mutate(., per_densite_w = ((round(densite_w, digits = 2) - 193.83)/193.83) * 100) -> belgique_per_densite_w
  
belgique_f_dense %>.%
  select(., - poptot) %>.%
  mutate(., per_densite_f = ((round(densite_f, digits = 2) - 425.31)/425.31) * 100) -> belgique_per_densite_f
  
bel_dense %>.%
  mutate(., per_densite_b = ((round(densite_b, digits = 2) - 326.57)/326.57) * 100) -> belgique_per_densite_b

per_bel_d1 <- full_join(belgique_regan, belgique_per_densite_bc, by = c("region", "annees"))
  
per_bel_d2 <- full_join(per_bel_d1, belgique_per_densite_w, by = c("region", "annees"))
  
per_bel_d3 <- full_join(per_bel_d2, belgique_per_densite_f, by = c("region", "annees"))

belgique_per_densite <- full_join(per_bel_d3, belgique_per_densite_b, by = c("region", "poptot", "annees"))

belgique_per_densite %>.%
  mutate(., 
    per_densite_f2 = str_replace_na(per_densite_f,replacement = ""),
    per_densite_w2 = str_replace_na(per_densite_w,replacement = ""),
    per_densite_bc2 = str_replace_na(per_densite_bc,replacement = ""),
    per_densite_b2 = str_replace_na(per_densite_b,replacement = "")
  ) %>%
  mutate(
    per_densite = str_c(per_densite_f2, per_densite_w2, per_densite_bc2, per_densite_b2)
  ) -> belgique_per_densite_clean

belgique_per_densite_clean <- select(belgique_per_densite_clean, - c("densite_bc", "per_densite_bc", "densite_w", "per_densite_w", "densite_f", "per_densite_f", "per_densite_f2", "per_densite_w2", "per_densite_bc2", "superf_b", "densite_b", "per_densite_b", "per_densite_b2"))

# Finish joint
belgique_densite_all <- full_join(belgique_densite_clean, belgique_per_densite_clean, by = c("region", "annees", "poptot"))
```
  
## Introduction
This post will explore the the increase rate of belgian population density by region between 1992 and 2019.
  
## Data spreadsheet and graph
```{r}
# Kable
options(knitr.table.format = NULL)
knitr::kable(belgique_densite_all, col.names = c("Années", "Région", "Population", "Densité (habitant/km^2)", "Taux de croissance de densité (%)"), align = "ccccc")
```

```{r}
chart(belgique_densite_all, as.numeric(per_densite) ~ as.numeric(annees) %col=% region) +
  geom_point() +
  geom_line() +
  theme(legend.position = "top", legend.text = element_text(size = 10), legend.justification = "center") +
  labs(y = "Increase rate of [habitant/km^2]", x = "Years", col = "", title = "Increase rate of belgian population density by region between 1992 - 2019")
```
  
## Analysis
Multiple important analysis can be made about this graph:
  
* Urbanisation is on the rise. Huge cities such as Brussels are undergoing a steep increase in their population density.
* The average increase rate of the belgian population density corresponds to the increase rate of the flemish population density.
* Wallonia's rate is decreasing due to massive urbanisation. A plateau is expected to be reached soon.





















